Pattern matching for\\ $(231,213)$-avoiding permutations

### 2015-02-05 article.tex
modification : typo

			There are two cases to consider searching for a match : \\
			If $n_\pmotif \in \x$ there exists a match
			if and only if\\ $\bigcup_{0<\min<\max<n_\ptext}\mathbb{P}_{\pmotif,\ptext,\min,\max}(0,0)$ is true.\\

			If $n_\pmotif \notin \x$ there exists a match if and only if \\	$\bigcup_{0<k<n_\ptext,0<\min<\max<n_\ptext}\mathbb{P}_{\pmotif,\ptext,\min,\max}(0,k)$
			is true.			
			\end{proof}

>>>>

			There are two cases to consider searching for a match :
			\begin{itemize}
				\item If $n_\pmotif \in \x$ there exists a match if and only if there is a match starting with the first element of the text:\\ $\bigcup_{0<\min<\max<n_\ptext}\mathbb{P}_{\pmotif,\ptext,\min,\max}(0,0)$ is true.
				\item If $n_\pmotif \notin \x$ there exists a match if and only if there exists a match stating at any index: \\	$\bigcup_{0<k<n_\ptext,0<\min<\max<n_\ptext}\mathbb{P}_{\pmotif,\ptext,\min,\max}(0,k)$
							is true.	
			\end{itemize}

			\end{proof}
